Parsing Postfix Log Files

### 2009-08-28 doc/logparser-results.tex
Required by Howard Hamilton: * Changed "most optimal" to "optimal". * Reviewed use of the word "optimal".

    \item [Optimal]  The most optimal order, according to the hypothesis:
        rules that recognise log lines most often will be used first.

    \item [Shuffle] This ordering is intended to represent a randomly
        ordered ruleset.  The rules will be shuffled once before use and
        will retain that ordering until the parser exits.  Note that the
        ordering will change every time the parser is executed, so 10
        different rule orderings will be generated for each log file in the
        test run.

>>>>

    \item [Optimal]  The optimal order, according to the hypothesis: rules
        that recognise log lines most frequently will be used first.

    \item [Shuffled] This ordering is intended to represent a randomly
        ordered ruleset.  The rules will be shuffled once before use and
        will retain that ordering until the parser exits.  Note that the
        ordering will change every time the parser is executed, so 10
        different rule orderings will be generated for each log file in the
        test run.
